Graph Neural Networks For Multi-Image Matching

### 2019-06-12 latex/iccv2019/rebuttal/egrebuttal.tex

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{iccv_rebuttal}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\iccvPaperID{****} % *** Enter the ICCV Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{\LaTeX\ Guidelines for Author Response}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section{Introduction}
Thank you to all the reviewers for all of your constructive comments and feedback.
We will fix all the minor typos and misunderstandings you have pointed out. 
We hope to point out the more important points here.
% Thank you to all the reviewers for all of your constructive comments and feedback. We fully understand your concerns and we elaborate on them here. We kindly ask you to trust us that the presentation will be clear in the camera-ready and to reward the novelty of the idea in your ratings.

%-------------------------------------------------------------------------
\subsection{Reviewer 1}
\textit{Things are not what they seem}: This is an ominous quote that makes things appear much more dramatic.

%------------------------------------------------------------------------
\subsection{Reviewer 2}
\textit{So it has come to this}: This is another ominous quote that while basically vacuous makes everything appear much more dramatic.

%------------------------------------------------------------------------
\subsection{Reviewer 3}
\textit{So it begins}: This also is an ominous quote that applies to most beginnings but makes things appear much more dramatic.

% \begin{figure}[t]
% \begin{center}
% \fbox{\rule{0pt}{1.8in} \rule{0.9\linewidth}{0pt}}
%    %\includegraphics[width=0.8\linewidth]{egfigure.eps}
% \end{center}
%    \caption{Example of caption.  It is set in Roman so that mathematics
%    (always set in Roman: $B \sin A = A \sin B$) may be included without an
%    ugly clash.}
% \label{fig:long}
% \label{fig:onecol}
% \end{figure}

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2019-09-21 latex/iclr2020/main.tex
Added ICLR latex

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{iccv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \iccvfinalcopy % *** Uncomment this line for the final submission

\def\iccvPaperID{4115} % *** Enter the ICCV Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

%% Custom control sequences
\let\oldPr\Pr
\newcommand{\bR}{\mathbb{R}}
\renewcommand*{\Pr}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\mat}[1]{\mathbf{#1}}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand{\tr}{\mathbf{tr}}
\newcommand{\cross}[1]{[#1]_{\times}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ificcvfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE
\title{All Graphs Lead to Rome: Learning Geometric and Cycle-Consistent Representations with Graph Networks}

\author{Stephen Phillips, Kostas Daniilidis \\
GRASP Laboratory, University of Pennsylvania\\
{\tt\small \{stephi, kostas\}@seas.upenn.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
    Image feature matching is a fundamental part of many geometric computer vision applications, and using multiple images can improve performance.
    In this work, we formulate multi-image matching as a graph embedding problem then use a Graph Neural Network to learn an appropriate embedding function for aligning image features.
    We use cycle consistency to train our network in an unsupervised fashion, since ground truth correspondence is difficult or expensive to acquire.
    In addition, geometric consistency losses can be added at training time, even if the information is not available in the test set, unlike previous approaches which optimize cycle consistency directly.
    To the best of our knowledge, no other works have used learning for multi-image feature matching.
    Our experiments show that our method is competitive with other optimization based approaches.
\end{abstract}

@@

Feature matching is an essential part of Structure from Motion and many geometric computer vision applications.
The goal in multi-image feature matching is to take 2D image locations from three or more images and find which ones correspond to the same point in the 3D scene.
Methods such as SIFT feature matching \cite{lowe2004distinctive} followed by RANSAC \cite{fischler1981random} have been the standard for decades.
However RANSAC-based approaches are limited to matching pairs of images, which can lead to global inconsistencies in the matching.
% TODO: Mention trifocal tensors
Other works, such as Wang et al.~\cite{wang2017multi}, have shown improvement in performance by optimizing cycle consistency, i.e. enforcing the pairwise feature matches to be globally consistent, illustrated in figure \ref{fig:cycconsistex}.

@@

\begin{figure}[t]
\begin{center}
  % \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
  \includegraphics[width=0.8\linewidth]{figures-CycleConsistencyBasic-v2.pdf}
\end{center}
  \caption{
    Example of multi-image matching and cycle consistency, with images from Rome16K dataset \cite{li2010location}.
    Pairwise matches between image can lead to global inconsistencies in the matching.
    In this example, an error in matching leads to an inconsistent cycle (shown in red), ideally these pairwise matches would be consistent.
    We improve the quality of pairwise matches in the multi-view matching problem by training a neural net with cycle consistency.
  }
\label{fig:cycconsistex}
\label{fig:onecol}
\end{figure}

%------------------------------------------------------------------------
\begin{figure*}[t]
\begin{center}
  % \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
  \includegraphics[width=0.8\linewidth]{figures-CycleConsistencyMainFigure-v4.pdf}
\end{center}
  \caption{
    An illustration of the approach of this work.
    The Graph Neural Neural Network (GNN) \cite{battaglia2018relational} takes as input the graph of matches and then outputs a low rank embedding of the adjacency matrix of the graph.
    The GNN operates on an embedding over the vertices of the graph.
    In the figure, the GNN vertex embeddings are represented by different colors.
    The final embedding is used to construct a pairwise similarity matrix, which we train to be a low dimensional cycle-consistent representation of the graph adjacency matrix, thus pruning the erroneous matches.
    We train the network using a reconstruction loss on the similarity matrix with the noisy adjacency matrix, and thus do not need ground truth matches.
    In addition, we can use geometric consistency information, such as epipolar constraints, to assist training the network.
  }
\label{fig:pipeline}
\label{fig:onecol}
\end{figure*}

@@

\begin{figure}[t]
\begin{center}
  \includegraphics[width=0.9\linewidth]{figures-UniverseOfFeatures-v2.pdf}
\end{center}
  \caption{
    Illustration of the universe of features.
    Each feature in each image corresponds to a 3D point in the scene.
    We can construct cycle consistent embeddings of the features by mapping each one to the one-hot vector of its corresponding 3D point.
    While there can be many features, there are fewer 3D points and thus this corresponds to a low rank factorization of the correspondence matrix.
    Best viewed in color.
  }
\label{fig:universefeatures}
\label{fig:onecol}
\end{figure}
Our goal is to learn optimal features that capture multiple image views by filtering out noisy feature matches.
An outline of our approach can be seen in figure \ref{fig:pipeline}.
The input to our algorithm is a set of features and noisy correspondences, and the output is a new set of features where the pairwise similarities of these features correspond to the true matches.
We do this by training the new set of feature embeddings to be cycle consistent.
We formulate this problem in terms of the correspondence graph of the features.
Vectors $\mat{x}$ and matrices $\mat{A}$ are denoted with boldface, and the $i^{th}$ row of a matrix is denoted $(\mat{A})_i$.
Graphs $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ have a set of vertices $\mathcal{V}$ and of edges $\mathcal{E} \subseteq \mathcal{V} \times \mathcal{V}$.
Implicitly in the subsequent discussions we assume the edges are directed.
For a vertex $v \in \mathcal{V}$ we use $\mathcal{N}^{h}(v)$ to denote the $h$-hop neighbors of $v$, with the superscript left out for 1-hop neighbors.
Similarly $\mathcal{E}(v)$ is used to denote the edges associated with $v$.
To denote the vertices connected to an edge $e \in \mathcal{E}$ we write $e(v_1, v_2)$.
\subsection{Correspondence Graph}
We assume there is an initial set of feature matches represented as a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$, with an associated adjacency matrix $\mat{A}$.
The graph is constructed from putative correspondences of image features across images, typically constructed using feature descriptor distance (e.g. SIFT feature distance).
While there are many interesting methods for computing these putative correspondences \cite{suh2015subgraph, yi2018learning}, we do not explore them in this work.
Typically putative correspondences are matched probabilistically, meaning a feature in one image matches to many features in another.
The ambiguity in the matches could come from repeated structures in the scene, insufficiently informative low-level feature descriptors, or just an error in the matching algorithm.
Filtering out these noisy matches is our primary learning goal.

Each vertex of the graph $v \in \mathcal{V}$ is an image feature, corresponding to some ground truth 3D point $\mat{P}(v)$.
Each edge $e = (v_1, v_2) \in \mathcal{E}$ is a potential correspondence.
Associated with each vertex $v$ is an embedding $\mat{f}_v \in \bR^m$, which can include the visual feature descriptor, position, scale, orientation, etc.
Similarly, each edge $e$ has an associated feature $\mat{f}_e \in \bR^p$ (in this work, initially just the weight of the feature association).
We use these features as the initialization for our learning algorithm.

In the absence of noise or outliers, this graph would have a connected component for each visible point in the world, all mutually disjoint.
Without noise, vertices $v$ would only match with other vertices $v'$ that correspond to the same 3D point in the scene.
Since features in this case represent unique locations in the scene, no points in the same image would have edges $e$ between them.
Mathematically, this can be expressed as $e = (v_1, v_2) \in \mathcal{E} \implies \mat{P}(v_1) = \mat{P}(v_2)$.
In the noisy case we expect this structure to be corrupted, i.e. there are some edges $e = (v_1, v_2) \in \mathcal{E}$ such that $\mat{P}(v_1) \neq \mat{P}(v_2)$.
Thus we need to prune the erroneous edges.

@@

\subsection{Graph Neural Networks}
As input to our method we are given a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ with the features described last section $\mat{f}_v \forall v \in \mathcal{V}$ and $\mat{f}_e \forall e \in \mathcal{E}$.
As with any neural network, GNNs have layered outputs.
We describe the output of layer $k$ as $\mat{f}_v^{(k)} \in \bR^{m_k}\, \forall v \in \mathcal{V}$ and $\mat{f}_e^{(k)} \in \bR^{p_k}\, \forall e \in \mathcal{E}$, with the initial embeddings denoted $\mat{f}_v^{(0)} = \mat{f}_v$ and $\mat{f}_e^{(0)} = \mat{f}_e$.
It will be useful to write these features as matrices in later sections, so we denote the vertex embedding matrix as $\mat{F}_V^{(k)}$ and the edge embedding matrix as $\mat{F}_E^{(k)}$.
If a superscript is not specified then it refers to the final output of the network.

First we describe older methods of GNNs to give context, then we describe the method we use in this work.
Many older methods assume we have the adjacency matrix $\mat{A}$ of the graph known a-priori \cite{bruna2013spectral}, and can encode graph convolutions using the eigenvectors of $\mat{A}$.
However, we do not have this luxury, as the correspondence structure changes from image set to image set, and thus we use non-spectral Graph Neural Networks.
There are many variations on non-spectral methods, often which ultimately amount to message passing between vertices of the graph with learned non-linear transformations between various steps \cite{kipf2017semi, defferrard2016convolutional, gama2018mimo, gama2018convolutional}.
Some works such as \cite{gama2019convolutional} use pooling operations on the vertices to make the graph smaller and thus aid computation, but as we need labels on every vertex of the original graph, so we cannot use this.
Most of GNNs used in these works can be expressed mathematically as:
\begin{align*}
\mat{\tilde{f}}_v^{(k+1)} =&\; b^{(k)} + \mat{W}_0^{k} \mat{f}_{v}^{(k)} + \sum_{h=0}^H \sum_{v' \in \mathcal{N}^{h}(v)} f_{e(v,v')} \mat{W}_{h}^{k} \mat{f}_{v'}^{(k)} \\
\mat{f}_v^{(k+1)} =&\; \sigma\left(\mat{\tilde{f}}_v^{(k+1)}\right)
\end{align*}
The weights/biases $\mat{W}_{h}^{k}$, $b^{(k)}$ are all learned, with no learning done on the edge weights $f_{e(v,v')}$. 
Note that this is just sums or averages over $h$-hop neighborhoods, where the weights on the edges remain static through the computation.
Given that we are trying to prune edges, it would be sensible to add features over edges to learn which ones to prune and which to keep such as in \cite{scarselli2009graph}.

@@

Mathematically, this is expressed as: % TODO: Maybe make this MLP oriented?
\begin{align}
\mat{\tilde{f}}_{e(v_1,v_2)}^{(k+1)} =&\; \mat{U}_1^{(k)} \mat{f}_{e}^{(k)} + \mat{U}_1^{(k)} \mat{f}_{v_1}^{(k)} + \mat{U}_2^{(k)} \mat{f}_{v_2}^{(k)} \\
\mat{f}_{e(v_1,v_2)}^{(k+1)} =&\; \sigma \left(a^{(k)} + \mat{\tilde{f}}_{e(v_1,v_2)}^{(k+1)}\right) \\
\mat{\tilde{f}}_{v}^{(k+1)} =&\; \mat{W}_0^{(k)} \mat{f}_{v}^{(k)} + \sum_{e \in \mathcal{E}(v)} \mat{W}_1^{(k)} \mat{f}_{e}^{(k+1)} \\
\mat{f}_v^{(k+1)} =&\; \sigma\left(b^{(k)} + \mat{\tilde{f}}_v^{(k+1)}\right)
\end{align}
Here the learned weights are denoted $\mat{W}$ and $\mat{U}$, and the biases $a^{(k)}$ and  $b^{(k)}$.
In \cite{battaglia2018relational}, they allow for more sophisticated aggregation functions, but in this work we simply use the mean function.
In practice, we use MLPs in message passes between vertices and edges for better expressiveness

\begin{figure}[t]
\begin{center}
  \includegraphics[width=0.8\linewidth]{figures-GeometricConsistency-v2.pdf}
\end{center}
  \caption{
    Illustrated here is an example of how the geometric loss is computed for one feature.  
    Errors are computed via absolute distance from the epipolar line, as expressed by (\ref{eq:essential_constraint}) via the epipolar constraint.
    The epipolar line is the line of projection of the feature on the first image, projected onto to the second.
    The distance to this line on the second image indicates how likely that point is to correspond geometrically to the original feature.
    There can be false positives along the projected line, as shown by the square feature in the figure, but other points will be eliminated, such as the hexagonal feature.
    Best viewed in color.
  }
\label{fig:geoconsist}
\label{fig:onecol}
\end{figure}

@@

Let $\mat{M}$ be the noiseless set of matches between our features, with $\mat{M}_{ij}$ being the matches between image $i$ and image $j$.
If the pairwise matches are globally consistent, then we can say that, for all $i, j, k$:
\begin{equation}
\mat{M}_{ij} = \mat{M}_{ik} \mat{M}_{kj}
\label{eq:cycconsist1}
\end{equation}
In other words, the matches between two images stay the same no matter what path is taken to get there. 
This constraint is known as \textit{cycle consistency}, and has been used in a number of works to optimize for global consistency \cite{zhou2015multi, wang2017multi, leonardos2016distributed}.
Stated in this form, there are $O(n^3)$ cycle consistency constraints to check.
A more elegant way to represent cycle consistency is to first create a `universe' of features that all images match to (see figure \ref{fig:universefeatures}).
Then, one can match the $i^{th}$ set of features to the universe using a ground-truth matching matrix $\mat{X}_i$.
Then the cycle consistency constraint becomes:
\begin{equation}
\mat{M}_{ij} = \mat{X}_{i}\mat{X}_{j}^\top
\label{eq:cycconsist2}
\end{equation}

\begin{table*}
\begin{center}
\begin{tabular}{|l|c|c|}
\hline
Method & Same Point Similarities & Different Point Similarities  \\
\hline\hline\hline
Ideal                              & 1.00e+0 $\pm$ 0.00e+0 & 0.00e+0 $\pm$ 0.00e+0 \\ \hline
Initialization Baseline            & 5.11e-1 $\pm$ 1.68e-2 & 2.56e-1 $\pm$ 2.06e-1 \\ \hline
3 Views, Noiseless                 & 9.96e-1 $\pm$ 7.70e-3 & 1.16e-1 $\pm$ 1.32e-1 \\ 
5 Views, Noiseless                 & 1.00e+0 $\pm$ 4.15e-4 & 1.22e-1 $\pm$ 1.67e-1 \\ \hline
3 Views, Added Noise               & 9.96e-1 $\pm$ 7.70e-3 & 1.16e-1 $\pm$ 1.32e-1 \\ 
5 Views, Added Noise               & 9.89e-1 $\pm$ 2.47e-2 & 7.67e-2 $\pm$ 1.56e-1 \\ 
6 Views, Added Noise               & 9.84e-1 $\pm$ 3.16e-2 & 7.46e-2 $\pm$ 1.57e-1 \\ \hline
3 Views, 5\% Outliers              & 9.29e-1 $\pm$ 1.79e-1 & 1.41e-1 $\pm$ 1.48e-1 \\ 
3 Views, 10\% Outliers             & 9.27e-1 $\pm$ 1.79e-1 & 1.40e-1 $\pm$ 1.51e-1 \\ \hline

@@

This reduces the number of our constraints from $O(n^3)$ to $O(n^2)$.
We try to learn vertex embeddings $\mat{F}_V$ to approximate $\mat{X}$ - in other words the final embedding should be an encoding of the universe of features.
As we do not have the ground truth matches $\mat{M}$, we approximate it using the noisy adjacency matrix $\mat{A}$ of our correspondence graph. Thus our loss would be 
\begin{equation}
\mathcal{L}(\mat{A}, \mat{F}_V) = \mathcal{D}(\mat{A}, \mat{F}_V \mat{F}_V^\top)
\end{equation}
Here $\mathcal{D}$ could be an $L_2$ loss, $L_1$ loss, or many others. In this work, we use the $L_1$ loss. 
Note that because of this formulation, we can determine our embeddings only up to a rotation, as
\begin{equation}
\mat{E}R(\mat{E}R)^\top
= \mat{E}RR^\top\mat{E}^\top
= \mat{E}\mat{E}^\top
\label{eq:rotinvar}
\end{equation}
Thus when visualizing embeddings, we rotate them to make them more interpretable (see figure \ref{fig:embeddingsviz}).

@@

% Method (6 Views)                                     & $L_1$             & $L_2$             & Area under ROC    & Area Prec.-Recall & Time (sec)        \ \hline

>>>>

\documentclass{article} % For LaTeX2e
\usepackage{iclr2020_conference,times}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{subcaption}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{url}

\newcommand{\cross}[1]{[#1]_{\times}}
\setlength{\textfloatsep}{12pt plus 2pt minus 2pt}

\title{Graph Neural Networks For Multi-Image Matching}

% Authors must not appear in the submitted version. They should be hidden
% as long as the \iclrfinalcopy macro remains commented out below.
% Non-anonymous submissions will be rejected without review.

\author{Stephen Phillips, Kostas Daniilidis \\
School of Engineering and Applied Sciences \\
University of Pennsylvania \\
Pennsylvania, PA 19104, USA \\
\texttt{\{stephi, kostas\}@seas.upenn.edu} \\
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}

\maketitle

\begin{abstract}
    Image feature matching is a fundamental part of many geometric computer vision applications, and using multiple images can improve performance.
    In this work, we formulate multi-image matching as a graph embedding problem then use a Graph Neural Network to learn an appropriate embedding function for aligning image features.
    We use cycle consistency to train our network in an unsupervised fashion, since ground truth correspondence is difficult or expensive to acquire.
    In addition, geometric consistency losses can be added at training time, even if the information is not available in the test set, unlike previous approaches which optimize cycle consistency directly.
    To the best of our knowledge, no other works have used learning for multi-image feature matching.
    Our experiments show that our method is competitive with other optimization based approaches.
\end{abstract}

@@

Feature matching is an essential part of Structure from Motion and many geometric computer vision applications.
The goal in multi-image feature matching is to take 2D image locations from three or more images and find which ones correspond to the same point in the 3D scene.
Methods such as SIFT feature matching \cite{lowe2004distinctive} followed by RANSAC \cite{fischler1981random} have been the standard for decades.
However RANSAC-based approaches are limited to matching pairs of images, which can lead to global inconsistencies in the matching.
% TODO: Mention trifocal tensors
Other works, such as Wang et al.~\cite{wang2017multi}, have shown improvement in performance by optimizing cycle consistency, i.e. enforcing the pairwise feature matches to be globally consistent.

@@

% \begin{figure}[t]
% \begin{center}
%   % \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
%   \includegraphics[width=0.8\linewidth]{figures-CycleConsistencyBasic-v2.pdf}
% \end{center}
%   \caption{
%     Example of multi-image matching and cycle consistency, with images from Rome16K dataset \cite{li2010location}.
%     Pairwise matches between image can lead to global inconsistencies in the matching.
%     In this example, an error in matching leads to an inconsistent cycle (shown in red), ideally these pairwise matches would be consistent.
%     We improve the quality of pairwise matches in the multi-view matching problem by training a neural net with cycle consistency.
%   }
% \label{fig:cycconsistex}
% \end{figure}

%------------------------------------------------------------------------
\begin{figure*}[t]
\begin{center}
  % \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
  \includegraphics[width=0.8\linewidth]{figures-CycleConsistencyMainFigure-v4.pdf}
\end{center}
  \caption{
    An illustration of the approach of this work.
    The Graph Neural Neural Network (GNN) \cite{battaglia2018relational} takes as input the graph of matches and then outputs a low rank embedding of the adjacency matrix of the graph.
    The GNN operates on an embedding over the vertices of the graph.
    In the figure, the GNN vertex embeddings are represented by different colors.
    The final embedding is used to construct a pairwise similarity matrix, which we train to be a low dimensional cycle-consistent representation of the graph adjacency matrix, thus pruning the erroneous matches.
    We train the network using a reconstruction loss on the similarity matrix with the noisy adjacency matrix, and thus do not need ground truth matches.
    In addition, we can use geometric consistency information, such as epipolar constraints, to assist training the network.
  }
\label{fig:pipeline}
\end{figure*}

@@

\begin{figure}[t]
\begin{subfigure}[b]{.45\linewidth}
  \centering
  \includegraphics[width=0.95\linewidth]{figures-UniverseOfFeatures-v2.pdf}
  \caption{Illustration of the universe of features.}
  \label{fig:1a}
  \label{fig:universefeatures}
\end{subfigure}%
\begin{subfigure}[b]{.45\linewidth}
  \centering
  \includegraphics[width=0.95\linewidth]{figures-GeometricConsistency-v2.pdf}
  \caption{Illustrated here is an example of how the geometric loss is computed for one feature.}
  \label{fig:1b}
  \label{fig:geoconsist}
\end{subfigure}
\caption{
  \textbf{(a)} Each feature in each image corresponds to a 3D point in the scene.
  We can construct cycle consistent embeddings of the features by mapping each one to the one-hot vector of its corresponding 3D point.
  While there can be many features, there are fewer 3D points and thus this corresponds to a low rank factorization of the correspondence matrix.
  \textbf{(b)} Errors are computed via absolute distance from the epipolar line, as expressed by (\ref{eq:essential_constraint}) via the epipolar constraint.
  The epipolar line is the line of projection of the feature on the first image, projected onto to the second.
  The distance to this line on the second image indicates how likely that point is to correspond geometrically to the original feature.
  There can be false positives along the projected line, as shown by the square feature in the figure, but other points will be eliminated, such as the hexagonal feature.
  Best viewed in color.
}
\label{fig:1}
\end{figure}

Our goal is to learn optimal features that capture multiple image views by filtering out noisy feature matches.
An outline of our approach can be seen in figure \ref{fig:pipeline}.
The input to our algorithm is a set of features and noisy correspondences, and the output is a new set of features where the pairwise similarities of these features correspond to the true matches.
We do this by training the new set of feature embeddings to be cycle consistent.
We formulate this problem in terms of the correspondence graph of the features.
Graphs $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ have a set of vertices $\mathcal{V}$ and of edges $\mathcal{E} \subseteq \mathcal{V} \times \mathcal{V}$ and implicitly in the subsequent discussions we assume the edges are directed.
For a vertex $v \in \mathcal{V}$ we use $\mathcal{N}^{h}(v)$ to denote the $h$-hop neighbors of $v$, with the superscript left out for 1-hop neighbors.
Similarly $\mathcal{E}(v)$ is used to denote the edges associated with $v$.
To denote the vertices connected to an edge $e \in \mathcal{E}$ we write $e(v_1, v_2)$.
\subsection{Correspondence Graph}
We assume there is an initial set of feature matches represented as a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$, with an associated adjacency matrix $\mA$.
The graph is constructed from putative correspondences of image features across images, typically constructed using feature descriptor distance (e.g. SIFT feature distance).
While there are many interesting methods for computing these putative correspondences \cite{suh2015subgraph, yi2018learning}, we do not explore them in this work.
Typically putative correspondences are matched probabilistically, meaning a feature in one image matches to many features in another.
The ambiguity in the matches could come from repeated structures in the scene, insufficiently informative low-level feature descriptors, or just an error in the matching algorithm.
Filtering out these noisy matches is our primary learning goal.

Each vertex of the graph $v \in \mathcal{V}$ is an image feature, corresponding to some ground truth 3D point $\vp(v)$.
Each edge $e = (v_1, v_2) \in \mathcal{E}$ is a potential correspondence.
Associated with each vertex $v$ is an embedding $\vf_v \in \sR^m$, which can include the visual feature descriptor, position, scale, orientation, etc.
Similarly, each edge $e$ has an associated feature $\vf_e \in \sR^p$ (in this work, initially just the weight of the feature association).
We use these features as the initialization for our learning algorithm.

In the absence of noise or outliers, this graph would have a connected component for each visible point in the world, all mutually disjoint.
Without noise, vertices $v$ would only match with other vertices $v'$ that correspond to the same 3D point in the scene.
Since features in this case represent unique locations in the scene, no points in the same image would have edges $e$ between them.
Mathematically, this can be expressed as $e = (v_1, v_2) \in \mathcal{E} \implies \mP(v_1) = \mP(v_2)$.
In the noisy case we expect this structure to be corrupted, i.e. there are some edges $e = (v_1, v_2) \in \mathcal{E}$ such that $\mP(v_1) \neq \mP(v_2)$.
Thus we need to prune the erroneous edges.

@@

\subsection{Graph Neural Networks}
As input to our method we are given a graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ with the features described last section $\vf_v \; \forall v \in \mathcal{V}$ and $\vf_e \; \forall e \in \mathcal{E}$.
As with any neural network, GNNs have layered outputs.
We describe the output of layer $k$ as $\vf_v^{(k)} \in \sR^{m_k} \, \forall v \in \mathcal{V}$ and $\vf_e^{(k)} \in \sR^{p_k}\, \forall e \in \mathcal{E}$, with the initial embeddings denoted $\vf_v^{(0)} = \vf_v$ and $\vf_e^{(0)} = \vf_e$.
It will be useful to write these features as matrices in later sections, so we denote the vertex embedding matrix as $\mF_V^{(k)}$ and the edge embedding matrix as $\mF_E^{(k)}$.
If a superscript is not specified then it refers to the final output of the network.

First we describe older methods of GNNs to give context, then we describe the method we use in this work.
Many older methods assume we have the adjacency matrix $\mA$ of the graph known a-priori \cite{bruna2013spectral}, and can encode graph convolutions using the eigenvectors of $\mA$.
However, we do not have this luxury, as the correspondence structure changes from image set to image set, and thus we use non-spectral Graph Neural Networks.
There are many variations on non-spectral methods, often which ultimately amount to message passing between vertices of the graph with learned non-linear transformations between various steps \cite{kipf2017semi, defferrard2016convolutional, gama2018mimo, gama2018convolutional}.
Some works such as \cite{gama2019convolutional} use pooling operations on the vertices to make the graph smaller and thus aid computation, but as we need labels on every vertex of the original graph, so we cannot use this.
Most of GNNs used in these works can be expressed mathematically as:
\begin{align*}
\tilde{\vf}_v^{(k+1)} =&\; \sigma\left( b^{(k)} + \mW_0^{k} \vf_{v}^{(k)} + \sum_{h=0}^H \sum_{v' \in \mathcal{N}^{h}(v)} f_{e(v,v')} \mW_{h}^{k} \vf_{v'}^{(k)} \right) \\
\end{align*}
The weights/biases $\mW_{h}^{k}$, $b^{(k)}$ are all learned, with no learning done on the edge weights $f_{e(v,v')}$. 
Note that this is just sums or averages over $h$-hop neighborhoods, where the weights on the edges remain static through the computation.
Given that we are trying to prune edges, it would be sensible to add features over edges to learn which ones to prune and which to keep such as in \cite{scarselli2009graph}.

@@

Mathematically, this is expressed as: % TODO: Maybe make this MLP oriented?
\begin{align}
\tilde{\vf}_{e(v_1,v_2)}^{(k+1)} =&\; \sigma \left(a^{(k)} + \mU_1^{(k)} \vf_{e}^{(k)} + \mU_1^{(k)} \vf_{v_1}^{(k)} + \mU_2^{(k)} \vf_{v_2}^{(k)} \right) \\
\tilde{\vf}_{v}^{(k+1)} =&\; \sigma\left(b^{(k)} + \mW_0^{(k)} \vf_{v}^{(k)} + \sum_{e \in \mathcal{E}(v)} \mW_1^{(k)} \vf_{e}^{(k+1)} \right) 
\end{align}
Here the learned weights are denoted $\mW$ and $\mU$, and the biases $a^{(k)}$ and  $b^{(k)}$.
In \cite{battaglia2018relational}, they allow for more sophisticated aggregation functions, but in this work we simply use the mean function.
In practice, we use MLPs in message passes between vertices and edges for better expressiveness

@@

Let $\mM$ be the noiseless set of matches between our features, with $\mM_{ij}$ being the matches between image $i$ and image $j$.
If the pairwise matches are globally consistent, then for all $i, j, k$:
\begin{equation}
\mM_{ij} = \mM_{ik} \mM_{kj}
\label{eq:cycconsist1}
\end{equation}
In other words, the matches between two images stay the same no matter what path is taken to get there. 
This constraint is known as \textit{cycle consistency}, and has been used in a number of works to optimize for global consistency \cite{zhou2015multi, wang2017multi, leonardos2016distributed}.
Stated in this form, there are $O(n^3)$ cycle consistency constraints to check.
A more elegant way to represent cycle consistency is to first create a `universe' of features that all images match to (see figure \ref{fig:universefeatures}).
Then, one can match the $i^{th}$ set of features to the universe using a ground-truth matching matrix $\mX_i$.
Then the cycle consistency constraint becomes:
\begin{equation}
\mM_{ij} = \mX_{i}\mX_{j}^\top
\label{eq:cycconsist2}
\end{equation}

\begin{table*}[t]
\begin{center}
\begin{tabular}{|l|c|c|}
\hline
Method & Same Point Similarities & Different Point Similarities  \\
\hline\hline\hline
Ideal                              & 1.00e+0 $\pm$ 0.00e+0 & 0.00e+0 $\pm$ 0.00e+0 \\ \hline
Initialization Baseline            & 5.11e-1 $\pm$ 1.68e-2 & 2.56e-1 $\pm$ 2.06e-1 \\ \hline
3 Views, Noiseless                 & 9.96e-1 $\pm$ 7.70e-3 & 1.16e-1 $\pm$ 1.32e-1 \\ 
5 Views, Noiseless                 & 1.00e+0 $\pm$ 4.15e-4 & 1.22e-1 $\pm$ 1.67e-1 \\ \hline
3 Views, Added Noise               & 9.96e-1 $\pm$ 7.70e-3 & 1.16e-1 $\pm$ 1.32e-1 \\ 
5 Views, Added Noise               & 9.89e-1 $\pm$ 2.47e-2 & 7.67e-2 $\pm$ 1.56e-1 \\ 
6 Views, Added Noise               & 9.84e-1 $\pm$ 3.16e-2 & 7.46e-2 $\pm$ 1.57e-1 \\ \hline
3 Views, 5\% Outliers              & 9.29e-1 $\pm$ 1.79e-1 & 1.41e-1 $\pm$ 1.48e-1 \\ 
3 Views, 10\% Outliers             & 9.27e-1 $\pm$ 1.79e-1 & 1.40e-1 $\pm$ 1.51e-1 \\ \hline

@@

This reduces the number of our constraints from $O(n^3)$ to $O(n^2)$.
We try to learn vertex embeddings $\mF_V$ to approximate $\mX$ - in other words the final embedding should be an encoding of the universe of features.
As we do not have the ground truth matches $\mM$, we approximate it using the noisy adjacency matrix $\mA$ of our correspondence graph. Thus our loss would be 
\begin{equation}
\mathcal{L}(\mA, \mF_V) = \mathcal{D}(\mA, \mF_V \mF_V^\top)
\end{equation}
Here $\mathcal{D}$ could be an $L_2$ loss, $L_1$ loss, or many others. In this work, we use the $L_1$ loss. 
Note that because of this formulation, we can determine our embeddings only up to a rotation, as
$ \mE R(\mE R)^\top
= \mE RR^\top \mE^\top
= \mE\mE^\top
\label{eq:rotinvar} $
% Thus when visualizing embeddings, we rotate them to make them more interpretable (see figure \ref{fig:embeddingsviz}).

@@
